---
title: "Tallies"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: tufte::tufte_html
---

```{r setup, include=FALSE}
library(renv)
library(rvest)
library(dplyr)
library(tidyr)
library(lubridate)
library(purrr)
library(magrittr)
library(tibble)
library(stringr)
library(readr)
library(glue)
library(logr)
library(kableExtra)
library(tufte)
source("R/functions.R")
source("R/scrape_data.R")
source("R/totals_by_type.R")
source("R/per_event.R")
totals_by_system <- scrape_data()
```

This page provides the most recent tallies of [Oryx's excellent list of Russian and Ukrainian equipment losses](https://www.oryxspioenkop.com/2022/02/attack-on-europe-documenting-equipment.html) from the 2022 Russian Invasion of Ukraine^[https://en.wikipedia.org/wiki/2022_Russian_invasion_of_Ukraine].

## System Type

### Russia

```{r russia-total-system-type, echo=FALSE, warning=FALSE, message=FALSE}
totals_by_type() %>% dplyr::filter(country=="Russia") %>% knitr::kable(caption="Russia: Totals by System Type and Status") 
```

### Ukraine

```{r total-system-type, echo=FALSE, warning=FALSE, message=FALSE}
totals_by_type() %>% dplyr::filter(country=="Ukraine") %>% knitr::kable(caption="Ukraine: Totals by System Type and Status")
```

## By System

`r margin_note("Due to how the data is recorded, weapons systems may be recorded in here twice—*e.g.*, if it is listed as abandoned and captured, a system will be counted in both the abandoned and captured tallies.")`

### Russia 
```{r russia-total-system, echo=FALSE, warning=FALSE, message=FALSE}
total_by_system_wide(totals_by_system) %>% dplyr::filter(country=="Russia") %>% dplyr::arrange(desc(total)) %>% knitr::kable(caption="Russia: Totals by System and Status")
```

### Ukraine

```{r total-system, warning=FALSE, echo=FALSE, message=FALSE}
total_by_system_wide(totals_by_system) %>% dplyr::filter(country=="Ukraine") %>% dplyr::arrange(desc(total)) %>% knitr::kable(caption="Ukraine: Totals by System and Status")
```
