---
title: "Tallies"
date: "`r format(Sys.time(), '%d %B %Y')`"
output: html_document
---

```{r setup, include=FALSE}
# library(renv)
# library(rvest)
# library(dplyr)
# library(tidyr)
# library(lubridate)
# library(purrr)
# library(magrittr)
# library(tibble)
# library(stringr)
# library(readr)
# library(glue)
# library(logr)
# library(kableExtra)
# source("R/functions.R")
# source("R/scrape_data.R")
# source("R/totals_by_type.R")
# source("R/per_event.R")
# source("R/daily_count.R")
# totals_by_system <- scrape_data()
```

This page provides the most recent tallies of [Oryx's excellent list of Russian and Ukrainian equipment losses](https://www.oryxspioenkop.com/2022/02/attack-on-europe-documenting-equipment.html) from the 2022 Russian Invasion of Ukraine^[https://en.wikipedia.org/wiki/2022_Russian_invasion_of_Ukraine].

## Graphs
```{r daily_graph, fig.align='center', echo=FALSE, warning=FALSE, message=FALSE}
# daily_count <- daily_count()

graph_counts(daily_count, "All Types", "type_total")
```


## System Type {.tabset}

### Russia

```{r russia-total-system-type, echo=FALSE, warning=FALSE, message=FALSE}
totals_by_type() %>% dplyr::filter(country=="Russia") %>% kableExtra::kbl(caption="Russia: Totals by System Type and Status") %>% kableExtra::kable_classic(font_size=16)
```

### Ukraine

```{r total-system-type, echo=FALSE, warning=FALSE, message=FALSE}
totals_by_type() %>% dplyr::filter(country=="Ukraine") %>% kableExtra::kbl(caption="Ukraine: Totals by System Type and Status") %>% kableExtra::kable_classic(font_size=16)
```

## By System^["Due to how the data is recorded, weapons systems may be recorded in here twice—*e.g.*, if it is listed as abandoned and captured, a system will be counted in both the abandoned and captured tallies."]  {.tabset}

### Russia
```{r russia-total-system, echo=FALSE, warning=FALSE, message=FALSE}
total_by_system_wide(totals_by_system) %>% dplyr::filter(country=="Russia") %>% dplyr::arrange(desc(total)) %>% kableExtra::kbl(caption="Russia: Totals by System and Status") %>% kableExtra::kable_classic(font_size=16)
```

### Ukraine

```{r total-system, warning=FALSE, echo=FALSE, message=FALSE}
total_by_system_wide(totals_by_system) %>% dplyr::filter(country=="Ukraine") %>% dplyr::arrange(desc(total)) %>% kableExtra::kbl(caption="Ukraine: Totals by System and Status") %>% kableExtra::kable_classic(font_size=16)
```
