---
title: "Tallies"
date: "`r format(Sys.time(), '%d %B %Y')`"
author: "D. Scarnecchia"
format: 
  html:
    anchor-sections: true
---

```{r setup, include=FALSE}
# library(renv)
# library(rvest)
# library(dplyr)
# library(tidyr)
# library(lubridate)
# library(purrr)
# library(magrittr)
# library(tibble)
# library(stringr)
# library(readr)
# library(glue)
# library(logr)
# library(kableExtra)
source("R/functions.R")
source("R/scrape_data.R")
source("R/totals_by_type.R")
source("R/per_event.R")
source("R/daily_count.R")
```

This page provides the most recent tallies of [Oryx's excellent list of Russian and Ukrainian equipment losses](https://www.oryxspioenkop.com/2022/02/attack-on-europe-documenting-equipment.html) from the 2022 Russian Invasion of Ukraine[^1]. Up-to-date output datasets can be found at in the [oryx_data](https://github.com/scarnecchia/oryx_data) repo. This repo is updated automatically daily at 22:30 EDT/EST. The code for this tool can be downloaded at [scrape_oryx](https://github.com/scarnecchia/scrape_oryx/releases)

[^1]: [Wikipedia](https://en.wikipedia.org/wiki/2022_Russian_invasion_of_Ukraine)

## Graphs

```{r daily_graph, fig.align='center', echo=FALSE, warning=FALSE, message=FALSE}
graph_counts(daily_count, "All Types", "type_total")
```

## System Type {.tabset}

::: callout-important
Due to how the data is recorded, weapons systems may be recorded in here twice\-\--\*e.g.\*, if it is listed as abandoned and captured, a system will be counted in both the abandoned and captured tallies.
:::

### Russia

```{r russia-total-system-type, echo=FALSE, warning=FALSE, message=FALSE}
totals_by_type() %>%
  dplyr::filter(country == "Russia") %>%
  kableExtra::kbl(caption = "Russia: Totals by System Type and Status") %>%
  kableExtra::kable_classic(font_size = 16)
```

### Ukraine

```{r total-system-type, echo=FALSE, warning=FALSE, message=FALSE}
totals_by_type() %>%
  dplyr::filter(country == "Ukraine") %>%
  kableExtra::kbl(caption = "Ukraine: Totals by System Type and Status") %>%
  kableExtra::kable_classic(font_size = 16)
```

## By System {.tabset}

### Russia

```{r russia-total-system, echo=FALSE, warning=FALSE, message=FALSE}
total_by_system_wide(totals_by_system) %>%
  dplyr::filter(country == "Russia") %>%
  dplyr::arrange(desc(total)) %>%
  kableExtra::kbl(caption = "Russia: Totals by System and Status") %>%
  kableExtra::kable_classic(font_size = 16)
```

### Ukraine

```{r total-system, warning=FALSE, echo=FALSE, message=FALSE}
total_by_system_wide(totals_by_system) %>%
  dplyr::filter(country == "Ukraine") %>%
  dplyr::arrange(desc(total)) %>%
  kableExtra::kbl(caption = "Ukraine: Totals by System and Status") %>%
  kableExtra::kable_classic(font_size = 16)
```
